---
title: "Other statistical tests"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## "Please do stats test XYZ"

When you are collecting data for other modules, or in your Stage 3 projects, you
will often find that a member of staff is suggesting that you analyse your data
with a statistical test that you have not heard of. However, many of these 
'standard' statistical tests can be considered to be linear models. If you find
it less confusing to consider them as forms of linear models, then feel free to
stick to that. If you prefer to use the built-in R commands for each test, then
that is fine also. **What matters is the underlying hypothesis** that you are
trying to test. This will determine the exact structure of your `lm` or `glm`
function, or which built-in R command to use instead.

This website simply compares some of the commonly encounted statistical tests
in their __linear model__ format and their __built-in__ format. You can find
full details of this philosphy for teaching statistics at https://lindeloev.github.io/tests-as-linear/

### t-distribution
A lot of 'standard' statistical tests use the t-distribution, and you will often
here people refer to 't-tests', 'paired t-tests', 'one-sample t-tests'. These are
generally introduced early in statistics courses, as they are all relatively 
simple tests, although you have to know when to apply which one. A disadvantage is
that in Stage 3, when I ask students **"How are you planning to analyse your data?"**
the most common answer is **"Oh, perhaps a t-test"** because this is the first 
stats test they learnt and hence the easiest to remember. But first a quiz about
drinks (which yes, does link to t-tests)...

```{r quiz}
question("Which alcoholic beverage is related to the t-distribution?",
         answer("Smirnoff vodka"),
         answer("Rioja wine"),
         answer("Guiness stout", correct = TRUE),
         answer("Newcastle Brown Ale"),
         answer("Jameson's whiskey"),
         allow_retry = TRUE
)
```

Even if you managed to find the correct answer, you're probably puzzled (unless
you already know the strange story). Keep reading...
